---
title: "TCF4 promoter usage"
output: html_document
bibliography: citations.bib
---

Analysis of TCF4 promoter usage in RNA-Seq libraries derived from cell cultures of a PTHS patient and its respective parent.

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(rmarkdown)
library(proActiv)
library(GenomicFeatures)
```

---

List of STAR [@dobin_star_2013] junction files as input and create a vector describing experimental condition:

```{r}
files <- list.files("junction_files", full.names = TRUE)
condition <- rep(c("parent", "patient"), each = 3)
```

Create a Promoter Annotation object from a GENCODE 34 primary annotation GTF file:

```{r}
url <- "https://ftp.ebi.ac.uk/pub/databases/gencode/Gencode_human/release_34/gencode.v34.basic.annotation.gtf.gz"
tmp <- tempfile("gencode.v34.basic.annotation.gtf.gz")
download.file(url = url, destfile = tmp)
txdb <- makeTxDbFromGFF(tmp, format = "gtf")
promoterAnnotation <- preparePromoterAnnotation(txdb = txdb, species = "Homo_sapiens")
```


Execute the proActive [@demircioglu_pan-cancer_2019] analysis:

```{r message = FALSE}
result <- proActiv(files = files,
                   promoterAnnotation = promoterAnnotation,
                   condition = condition,
                   genome = "hg38")
rowData(result) %>%
  as_tibble() %>%
  filter(geneId == "ENSG00000196628.19") %>%
  paged_table()
```

Visualize the results in the TCF4 locus:

```{r}
plotPromoters(result, "ENSG00000196628.19", txdb)
```

## References

<div id="refs"></div>
<br>
